### 2021-08-31 documentos/pce.tex

Their construction include basically three ingredients: linearity, trace preserving and complete positivity.The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$
\subsection{Single qubit case} % {{{
% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
% mapas proyectivos, hay mapas proyectivos no unitales}
\todo{David escribe una primera version y luego Carlos itera}
\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}

>>>>

The construction of quantum channels includes basically three ingredients: linearity, trace preserving and complete positivity. The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$. The trace preserving is required for the process $\mcE$ to be deterministic, this is, $\tr\mcE[\rho]=\tr \rho =1$ with $\rho \in \mcS(\hilbert)$.
\subsection{Single qubit case} % {{{
% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
% mapas proyectivos, hay mapas proyectivos no unitales}
\todo{David escribe una primera version y luego Carlos itera}
\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}
